An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-04 scagnostics.Rmd
Updated pipe guided tour.

@@

```{r findpipe, results="hide"}
if(!file.exists("cache/findpipe.rda")){
  set.seed(1995)
  pipeResc <- rescale(pipe1000) 
  pipeTour <- save_history(pipeResc,
                          guided_tour(mineIndex("TIC"), search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
  pipeTourFull <- as.list(interpolate(pipeTour))
  save(pipeResc, pipeTour, pipeTourFull, file = "cache/findpipe.rda")
} else {
  load("cache/findpipe.rda")
}
```

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
if(!file.exists("cache/pipeFirstRun.rda")){
  pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
  pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
  save(pipeTourRes, pipeTourResMelt, file = "cache/pipeFirstRun.rda")
} else {
  load("cache/pipeFirstRun.rda")
}
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

>>>>

Double challengind: fine structure + (coherent) noise

@@

UPDATE: highlight times corresponding to new basis planes by red vertical line, as we approach the special view higher index values of TIC are often found on interpolated bases, this is why generally we want cooling but here we are trying to find overall maximum, but instead have good chance of finding a plane close to the special view allowing optimisation in a second step
By no means stable procedure, when changing seed we easily end up not finding special view but rather end up with plane that is not useful for further optimisation to identify pipe view.

```{r findpipe, results="hide"}
if(!file.exists("cache/findpipe.rda")){
  set.seed(1984)
  pipeResc <- rescale(pipe1000) 
  pipeTour <- save_history(pipeResc,
                          guided_tour(mineIndex("TIC"), search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
  pipeTourFull <- as.list(interpolate(pipeTour))
  save(pipeResc, pipeTour, pipeTourFull, file = "cache/findpipe.rda")
} else {
  load("cache/findpipe.rda")
}
```

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
if(!file.exists("cache/pipeFirstRun.rda")){
  pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
  pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
  save(pipeTourRes, pipeTourResMelt, file = "cache/pipeFirstRun.rda")
} else {
  load("cache/pipeFirstRun.rda")
}
newBasisPipeTour <- which(attributes(interpolate(pipeTour))$new_basis)
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")+
  geom_vline(data=as.tibble(newBasisPipeTour), mapping=aes(xintercept=value), color="red")
```
